Fasano--Franceschini Test: an Implementation of a 2-Dimensional Kolmogorov--Smirnov in \proglang{R}

### 2021-06-10 journalMS/article.tex
add FF test benchmarking

\subsection{Computational efficency}
\RBnote{This is weird without any data.  Can you benchmark using your package without bootstrap; your package with bootstrap and varying cores; and Peacock.test package to illustrate scaling?}
The main distinction between the Peacock and Fasano--Franceschini tests is in computational efficiency, as
illustrated by the benchmarking studies in \cite{Lopes2007}.  Briefly,
%\begin{itemize}
%\item The Fasano--Franceschini test runs in $O(n^2)$ time, and is advantageous to the Peacock test as data set sizes scale.
%\item The Peacock test is more computationally expensive, and runs in $O(n^3)$ time.
%\end{itemize}
the Fasano--Franceschini test runs in $O(n^2)$ time, and is advantageous to the Peacock test as data set sizes scale, while the Peacock test is more computationally expensive, and runs in $O(n^3)$ time.
%
(See the \pkg{Peacock.test} package for \proglang{R} implementation of the Peacock test.)

>>>>

\subsection{Computational efficency}

\begin{figure}[hbt]
\centering
\includegraphics{benchmark}
\caption{\label{fig:bmark} \textbf{A:} Benchmarking of the Fasano--Franceschini versus the Peacock test under four distinct numbers of points N (e.g. 10, 100, 1000, 5000). Points represent the average of 10 replicate runs. \textbf{B:} Benchmarking of Fasano--Franceschini test bootstrapping procedure broken up by the number of points N (e.g. 10, 100, 1000, 5000). Within each panel, lines are colored by the number of bootstraps run (e.g. 0, 10, 100, 1000). Points represent the average of 10 replicate runs.
}
\end{figure}

The main distinction between the Peacock and Fasano--Franceschini tests is in computational efficiency, as
illustrated by the benchmarking studies in \cite{Lopes2007}. Briefly,
the Fasano--Franceschini test runs in $O(n^2)$ time, and is advantageous to the Peacock test as data set sizes scale, while the Peacock test is more computationally expensive, and runs in $O(n^3)$ time (\textbf{Figure~\ref{fig:bmark}A}). While the implentation of the bootstrapping procedure increases runtime in comparison to the approximate fit from  \citep{numericalRecipes}; parallelization of the Fasano--Franceschini test shows $\sim 4X$ reduction in run time from 1 to 8 cores across bootstraps and number of points. \textbf{Figure~\ref{fig:bmark}B}.
%
(See the \pkg{Peacock.test} package for \proglang{R} implementation of the Peacock test.)
